---
title: "deeplyr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, eval = T, message = F, warning = F, error = F)
```

```{r, echo = F, results='asis'}
library(badger)
cat(
	badge_code_size("systats/deeplyr"),
	badge_last_commit("systats/deeplyr")
)
```


This package provides a simple interface for several third party machine learning libraries. Beside relational data and boosted trees a special focus is given to Natural Language Processing by gathering certain types of modern neural network architectures. 

```{r}
pacman::p_load(tidyverse, purrrr, tidyr)
```


Thanks to rapid open source development of popular machine learning libraries we able to fall back to on a wide variety of frameworks and model architectures. Of course your data project most likely requires some modifications to any given model, but browsing the main code blcoks allows to compose a suitable architecture. A short list can be seen here: 

```{r}
deeplyr::list_keras_models()
```

How to view a specific model arch?

```{r}
deeplyr::list_keras_models("bi_lstm")$model
```



<!-- This is a light-weight model engine mainly for text classification tasks written as R6class. While Keras, XGBoost or Ranger (RF) provide high quality learners, `deeplyr` comes with unifying train/test/report functions for all backends mentioned. This streamlined data/ model worklfow does automatically  -->


```{r}
# devtools::document()
# devtools::install()
```

